Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-03-12 eswc-2012/phdsymp.tex
systematic approach
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@176 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

A systematic approach based on statistical experimental design would
imply that all possible axes of variation are identified, to identify
possible contributions from different hardware platforms, operating
system constraints, backend tuning, triple store features, to SPARQL
language features and protocols. To make this benchmark feasible most
variations of parameters must be done by a software suite designed for
this purpose as the number of experiments that results will be very
large.
